Utilizing Parallel Workers: \\LLVM's Vectorization Plan

### 2024-11-23 paper/paper.tex
paper

Figure~\ref{fig:inner-loop-scalar-ir} shows the IR of the main loop basic blocks \texttt{for.body},
\texttt{if.then}, and \texttt{for.inc}. Figure~\ref{fig:inner-loop-vplan-hcfg-body} shows the equivalent
hierarchical control-flow-graph (CFG) of a VPlan modelling a vectorization approach for this 
scalar loop. Other basic blocks like the scalar epilogue loop and it's predication check (is the final
vector trip count equal to the original trip count) are omitted. See Figure~\ref{fig:inner-loop-vplan-hcfg}
in Appendix~\ref{appendix-figures} for the fully modeled HCFG.

@@

%TODO: Combine inner-loop-scalar-ir figure and inner-loop-vplan-hcfg into a single
%       double column figure.
\begin{figure}
  \centering
  \includegraphics[width=0.475\textwidth]{images/inner-loop-scalar-loop-ir-color.png}
  \caption{The scalar IR for the main loop part of the conditional loop depicted in
  Figure~\ref{fig:inner-loop-vec}. Note that \texttt{getelementptr inbounds}
  was abbreviated to \texttt{getelmptr inbs}.}
  \label{fig:inner-loop-scalar-ir}
\end{figure}

>>>>

Figure~\ref{fig:inner-loop-scalar-ir} shows the scalar IR of the main loop basic blocks \texttt{for.body},
\texttt{if.then}, and \texttt{for.inc}. Figure~\ref{fig:inner-loop-vplan-hcfg-body} shows the equivalent
hierarchical control-flow-graph (CFG) of a VPlan modelling a vectorization approach for this 
scalar loop. Other basic blocks like the scalar epilogue loop and it's predication check (is the final
vector trip count equal to the original trip count) are omitted. See Figure~\ref{fig:inner-loop-vplan-hcfg}
in Appendix~\ref{appendix-figures} for the fully modeled HCFG.

%TODO: Combine inner-loop-scalar-ir figure and inner-loop-vplan-hcfg into a single
%       double column figure.

\begin{figure}
  \centering
  \includegraphics[width=0.475\textwidth]{images/inner-loop-scalar-loop-ir-color.png}
  \caption{The scalar IR for the main loop part of the conditional loop depicted in
  Figure~\ref{fig:inner-loop-vec}. Note that \texttt{getelementptr inbounds}
  was abbreviated to \texttt{getelmptr inbs}.}
  \label{fig:inner-loop-scalar-ir}
\end{figure}

The different colored parts in the scalar IR can be found with the same color in the modeled VPlan.
The only completely new part that VPlan models in this example is the handling of the scalar epilogue
loop (purple).

@@
